Reply to: 2022-05603 Intentional release of native species undermines ecological stability

### 2022-10-21 rmd/manuscript.Rmd
rmd

Massive releases of captive-bred native species ("intentional release") is a pervasive method to enhance wild populations of commercial and recreational species. However, such external inputs may disrupt the sensitive species interactions that allow competing species to coexist, potentially compromising long-term community stability. Here, we use theory and long-term data of stream fish communities to show that intentional release destabilizes community dynamics with a limited demographic benefit to the enhanced species. Our theory predicted that intentional release intensifies interspecific competition, facilitating the competitive exclusion of unenhanced species that otherwise stably coexist. In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition. Consequently, the ecological community with the intentional release is predicted to show reduced community density with unstable temporal dynamics. Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery salmon - a major fishery resource worldwide. Our findings alarm that the current overreliance on intentional release may accelerate global biodiversity loss, threatening the provisioning of ecosystem services.

@@

The intentional release of captive-bred individuals is a common practice for conservation and natural resource management. However, we know little about its potential consequences for the whole ecological community. Here, we show that the intentional release undermines community stability with little demographic benefit to the enhanced species. Theory and data agree that intentional release destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species. The effect size of the intentional release was striking in its magnitude, doubling temporal fluctuations of enhanced communities compared to those with no intentional release. Our findings point to major limitations of intentional release as a primary tool for biodiversity conservation and sustainability.

@@

Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010]. Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010]. In particular, the magnitude of intentional release for commercial and recreational species is massive (reviewed in [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]) -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (bivalves, insects) [@ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually. There is growing awareness that intentional release entails ecological risks, such as the accumulation of deleterious alleles and the intensified competition within the enhanced species [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007; @kitadaLessonsLearnedJapanese2006]. Yet, this method is still pervasive in natural resource management owing to the significant economic benefit [@malkamakiSystematicReviewSocioeconomic2018; @davidEconomicFeasibilityIntensification2018; @rutledgeCostBenefitHatcheryreared1990; @kitadaEconomicEcologicalGenetic2018]. For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed the economic performance of release programs for 12 major fishery resources across the globe. The gross monetary yield exceeded the seed-production cost in nine species, suggesting that release programs are economically profitable in general.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** \@ref(fig:figure-layout)**E**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records. The release of masu salmon began in the 1950s, with the annual average ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019. The majority of release occurs in spring at fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset). Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for the potential effects of climates and local abiotic factors.

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate as the number of generations in captivity increases [@arakiGeneticEffectsCaptive2007]. Typically, hatchery masu salmon are reared in captivity for two to four generations. Given the duration of the extensive release program (\> 60 years), it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

>>>>

Massive releases of captive-bred native species ("intentional release") is a pervasive method to enhance wild populations of commercial and recreational species. However, such external inputs may disrupt the sensitive species interactions that allow competing species to coexist, potentially compromising long-term community stability. Here, we use theory and long-term data of stream fish communities to show that intentional release destabilizes community dynamics with a limited demographic benefit to the enhanced species. Our theory predicted that intentional release intensifies interspecific competition, facilitating the competitive exclusion of unenhanced species that otherwise stably coexist. In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition. Consequently, the ecological community with the intentional release is predicted to show reduced community density with unstable temporal dynamics. Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive release of hatchery salmon -- a major fishery resource worldwide. Our findings alarm that the current overreliance on intentional release may accelerate global biodiversity loss with undesired consequences for the provisioning of ecosystem services.

@@

The intentional release of captive-bred individuals is a common practice for conservation and natural resource management. However, we know little about its potential consequences for the whole ecological community. Here, we show that the intentional release undermines community stability with limited demographic benefit to the enhanced species. Theory and data agree that intentional release destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species. The effect size of the intentional release was striking in its magnitude, doubling temporal fluctuations of enhanced communities compared to those with no intentional release. Our findings point to major limitations of intentional release as a primary tool for conservation and sustainability.

@@

Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010]. Releases of captive-bred native species ("intentional release") is a form of the efforts to enhance wild populations of diverse taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010]. In particular, the magnitude of intentional release for commercial and recreational species is massive [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018] -- a single program releases up to tens of millions of plant [@laikreReleaseAlienPopulations2006], invertebrate (crustaceans, bivalves, insects) [@kitadaEconomicEcologicalGenetic2018; @ingsBumblebeesHumblePollinators2005; @haagNorthAmericanFreshwater2012], and vertebrate individuals (fish, birds) [@negroRAPDAnalysisDetection2001; @kitadaEconomicEcologicalGenetic2018] into the wild annually. There is growing awareness that intentional release entails ecological risks, such as the accumulation of deleterious alleles and the intensified competition within the enhanced species [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007; @kitadaLessonsLearnedJapanese2006]. Yet, this method is still pervasive in natural resource management owing to the significant economic benefit [@malkamakiSystematicReviewSocioeconomic2018; @davidEconomicFeasibilityIntensification2018; @rutledgeCostBenefitHatcheryreared1990; @kitadaEconomicEcologicalGenetic2018]. For example, Kitada @kitadaEconomicEcologicalGenetic2018 analyzed the economic performance of release programs for 12 major fishery resources across the globe. The gross monetary yield exceeded the seed-production cost in nine species, suggesting that release programs are economically profitable in general.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure** \@ref(fig:figure-layout)**E**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (all separated by the ocean; **Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official release records. The release of masu salmon began in the 1950s, with the annual average ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019. The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset). Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for the potential effects of climates and local abiotic factors.

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007]. Typically, masu salmon are reared in captivity for two to four generations. In light of the 60-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

### 2022-10-21 rmd/reply_r1.Rmd
rmd

1.  **Improve the introduction and implications**: both reviewers noted an absence of context in the previous manuscript. We agree with this comment. We revised the text to contextualize our work better to address this issue. In particular, we have carefully reviewed cases to which our findings may apply and discussed the relevance of our work to those systems.
2.  **Two-species simulation.** The editor suggested including a two-species simulation to guide the full community model. We appreciated this suggestion and were able to draw deeper insights into our theoretical analysis. At the same time, this improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis). We revised the Methods and Results following this change. In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
3.  **Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial; we agree with this comment. We have enriched the text pertinent to this issue. We have greatly increased the number of citations and discussed possible mechanisms (e.g., diet overlap, exploitative competition) that may produce the observed patterns more carefully. In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities. The estimated parameter indicated that competition among species certainly exists.
4.  **Life history of masu salmon.** Lastly, we enriched the text for the life history of masu salmon and how release programs for this species are operated.

In summary, the improved text/analysis provided clearer evidence that intentional release has destabilizing effects and clarified its broader relevance to other systems. We appended a point-by-point response below. We hope our manuscript is now suitable for publication in your journal.

@@

> Agreed. We have greatly improved the introduction and Discussion (paragraph L185 --, paragraph L209 --). We have clarified that our findings seem quite general for two reasons. (1) the scale of other release programs (mussels, crustaceans, birds, insects, and other fish) is generally way larger than our release program. For example, the largest release program for pink salmon in Alaska releases \> 600 million fish year^-1^ (note: our program releases only 0.24 million fish per year at the most intense site). (2) Most release programs aim to help declining populations in degraded habitats. In these habitats, the carrying capacities are likely compromised - a theoretical premise for the destabilizing effect to emerge.

@@

> We have addressed the concerns raised by the reviewers. Please see our response to specific comments. Also, we have improved our regression analysis to account for the spatial overlap of hatchery salmon and other wild fishes. Since we do not have exact information on where hatchery fish are released (we have partial information -- updated our map to include this information; see Figure 1C), we performed the *post hoc* estimation of spatial overlap within the regression model (see Methods, "effective release"). We believe this will increase the validity of our results as it enabled us to use 97 site replicates fully to estimate the effect of releases.

@@

> Thank you for the great comment! As you can see in our response to the editor's comment, we have greatly improved the introduction and Discussion (paragraph L208 --). We believe our findings are broadly applicable across taxa and ecosystems.

@@

> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (paragraph L184 --).

@@

> Good point -- unfortunately, we do not have any data to show quantitative patterns. The "hatchery" gene has likely spread within the wild populations, given the duration of the extensive release programs. We have briefly mentioned this in the revised text (paragraph L169 --).

@@

> We have detailed species information in Table S2. Masu salmon often co-occur with white-spotted charr, sculpins, and stone loaches. Since our watersheds are "protected" watersheds, any form of exploitation (including angling) is not allowed (regardless of fish species). Therefore, other factors are unlikely to shape the observed patterns of temporal community variability. Please note that we have statistically accounted for natural variations in land use, watershed size, climate etc.

@@

> We agree that our results are not surprising -- we are not surprised either. However, we strongly believe that our result is important and worth publishing because, to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long term. Also, perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)! This magnitude is way larger than the release program in our study system. Therefore, release numbers of $5\times$ carrying capacity seem conservative to us. Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative rather than an unrealistic extreme scenario.
>
> Regarding the competition coefficient, please find that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition -- i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species). The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence without intentional release. Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions. In the revised text, we have also provided empirical estimates of species interactions -- the median value was 0.29, so our simulation setup is reasonable.

@@

> Thank you for this comment. We agree that this pattern is important, and we acknowledge that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**). However, our focus here is not the influence of intentional release on the enhanced species -- we are interested in how unenhanced species respond to the intentional release. This is the knowledge gap we are trying to fill, as no study has focused on this "side-effect" of intentional release. We hope the reviewer will understand the significance of this finding.

@@

> Thank you, we agree that a detailed life-history model will provide useful insights into salmon management. However, we decided not to perform this analysis for the following reasons. First, given the readership of PNAS and the suggestions from reviewer 1 and the editor, we believe it is important to keep our model as general as possible. In fact, as clarified in the revised manuscript, there are many cases where our phenomenological model may apply. Second, Morita et al. have already developed a detailed life-history model [@moritaTemperaturedependentVariationAlternative2014]. Readers interested in the specifics of masu salmon can refer to this article. We have cited it in the revised manuscript. Lastly, we believe the reviewer misread our results in the previous manuscript. Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best. This result remains the same in the improved analysis in the revised manuscript. Therefore, there is little evidence supporting the importance of detailed life-history processes in explaining long-term population dynamics for our dataset.

@@

> We are glad that the reviewer caught this issue. We improved as follows:
>
> \- Enriched the text explaining masu salmon's life history; they spend at least one year in freshwater.
>
> \- Added species traits to Table S2.
>
> \- Added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix).
>
> As we clarified in the revised text, we are pretty sure that (hatchery) masu salmon interact with other species. Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches). In addition, numerous research documents competition between masu salmon and other stream fish species. We have clarified these points in the revised manuscript.

@@

> We appreciate the careful reading by the reviewer. This insightful comment helped a lot to avoid delivering the wrong messages. We agree and have substantially improved the introduction and Discussion to address this issue. Specifically, we now recognize that there are many cases where stock enhancement is economically successful -- we have mentioned these examples to develop a context properly. Also, where applicable, we have softened the language throughout the manuscript. If there are information/issues that we have missed, please let us know, and we will address them too.

>>>>

1.  **Improve the Introduction and implications**: both reviewers noted an absence of context in the previous manuscript. We agree with this comment. We revised the text to contextualize our work better. In particular, we have carefully reviewed cases to which our findings may apply and discussed the relevance of our work to those systems.
2.  **Two-species simulation.** The editor suggested including a two-species simulation to guide the full community model. We appreciated this suggestion and were able to draw deeper insights into our theoretical analysis. At the same time, this improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis). We revised the Methods and Results following this change. In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
3.  **Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial; we agree with this comment. We have enriched the text pertinent to this issue. We have greatly increased the number of citations and discussed possible mechanisms (e.g., diet overlap, exploitative competition) that may produce the observed patterns more carefully. In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities. The estimated parameter indicated that competition among species certainly exists.
4.  **Life history of masu salmon.** Lastly, we enriched the text for the life history of masu salmon and how release programs for this species are operated.

In summary, the improved text/analysis provides clearer evidence that intentional release has destabilizing effects and clarifies its broader relevance to other systems. We appended a point-by-point response below. We hope our manuscript is now suitable for publication in your journal.

@@

> Agreed. We followed your guidance to improve the Introduction and Discussion (**paragraph L185 --, paragraph L209 --**). In short, we have clarified the following point:
>
> Introduction -- We have included representative works that report the scale of intentional release for commercial and recreational species. The release programs included plants, insects, mollusks, crustaceans, fish, birds, and others. The magnitude was enormous, releasing several tens of thousands to \> 10 millions of individuals annually. Thus, our system certainly represents a typical scenario of release programs (our program releases 0.24 million fish per year at the most intense watershed).
>
> Discussion -- Given the scale of other release programs, our results should represent a conservative estimate of community-level impacts. In addition, many programs release individuals into "unsuitable" habitats to aid declining populations -- these programs are likely to cause the destabilizing effect of the intentional release because the carrying capacities of such habitats are likely compromised. We have clarified this point in the revised manuscript.
>
> Discussion -- We have also clarified that our findings align with previous work on other hatchery programs (including salmons and other fisheries). The decline of wild stocks has been repeatedly observed after intensive stocking (consistent with our theoretical predictions and empirical patterns). We have cited an important meta-analysis [@arakiHatcheryStockingHelp2010] along with several specific examples (e.g., pink salmon in Alaska, where \> 600 million fish year^-1^ are released).

@@

> Agreed. We have included more information on our study system. Please see our response to reviewer comments.
>
> Also, we have improved our regression analysis to account for the spatial overlap of hatchery salmon and other wild fishes. Since we do not have exact information on where and how many hatchery fish are released within a watershed (we are sure they are released near the fish survey sites though), we performed the *post hoc* estimation of spatial overlap within the regression model (see Methods, "effective release"). We believe this will increase the validity of our results as it enabled us to use 97 site replicates fully to estimate the effect of releases.

@@

> Thank you for the great comment! As you can see in our response to the editor's comment, we have greatly improved the Introduction and Discussion. We believe our findings are broadly applicable across taxa and ecosystems.

@@

> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (**paragraph L185 --**).

@@

> Good point -- however, we do not have any data to show quantitative patterns. The "hatchery" gene has likely spread within the wild populations, given the duration of the extensive release programs. We have briefly mentioned this in the revised text (**paragraph L170 --**).

@@

> We have detailed species information in Table S2 and have provided a co-occurrence matrix in Fig S16. Masu salmon often co-occur with white-spotted charr, sculpins, and stone loaches. Since our watersheds are "protected", any form of exploitation (including angling) is not allowed (regardless of species). Therefore, intentional release is the most likely explanation for the observed pattern. Please note that we have statistically accounted for natural variations in land use, watershed size, climate etc -- the effect size of these factors were smaller compared with the release effect.

@@

> We agree that our results are not surprising -- we are not surprised either. However, we believe that our result is important and worth publishing because, to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long term. Also, perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)! Therefore, release numbers of $5\times$ carrying capacity seem conservative to us. Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a typical scenario of release programs.
>
> Regarding the competition coefficient, please find that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition -- i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species). The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence without intentional release. Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions. In the revised text, we have also provided empirical estimates of species interactions -- the median value was 0.29, so our simulation setup is reasonable.

@@

> Thank you for this comment. We agree that this pattern is important, and we acknowledged that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**). However, our focus here is not the influence of intentional release on the enhanced species -- we are interested in how unenhanced species respond to the intentional release. This is the knowledge gap we are trying to fill, as no study has focused on this "side-effect" of intentional release. We hope the reviewer will understand the significance of this finding.

@@

> We agree that a detailed life-history model will provide useful insights into salmon management. We appreciate this comment. However, we decided not to perform this analysis for the following reasons. First, given the readership of PNAS and the suggestions from reviewer 1 and the editor, we believe it is important to keep our model as general as possible. In fact, as clarified in the revised manuscript, there are many cases where our phenomenological model may apply. Second, Morita et al. have already developed a detailed life-history model [@moritaTemperaturedependentVariationAlternative2014]. Readers interested in the specifics of masu salmon can refer to this article. We have cited it in the revised manuscript. Lastly, we believe the reviewer misread our results in the previous manuscript (correct us if we misunderstood something). Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best. This result remains the same in the improved analysis in the revised manuscript. Therefore, there is little evidence supporting the importance of detailed life-history processes in explaining long-term population dynamics for our dataset.

@@

> We are glad that the reviewer caught this issue. We improved as follows:
>
> \- Enriched the text explaining masu salmon's life history; they spend at least one year in freshwater.
>
> \- Added species traits to Table S2.
>
> \- Added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix).
>
> As we clarified in the revised text, we are pretty sure that (hatchery) masu salmon interact with other species. Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches). In addition, numerous research document competition between masu salmon and other stream fish species. We have clarified these points in the revised manuscript.

@@

> We appreciate the careful reading by the reviewer. This insightful comment helped a lot to avoid delivering the wrong messages. We agree and have substantially improved the Introduction and Discussion to address this issue. Specifically, we now recognize that there are many cases where stock enhancement is economically successful -- we have mentioned these examples to develop a context properly. Also, where applicable, we have softened the language throughout the manuscript. If there are information/issues that we have missed, please let us know, and we will address them too.

### 2022-10-21 rmd/supporting_info.Rmd
rmd

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 10.5pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
nocite: |
  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
---

@@

**Fish release.** The release of masu salmon began in the 1950s. Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Most fish are released near the fish survey sites. However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable. For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

>>>>

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 10.5pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.35\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
nocite: |
  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
---

@@

**Fish release.** The release of masu salmon began in the 1950s. Hatchery fish are reared in captivity for zero (wild origin) to seven generations (the majority is two to four generations). Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Most fish are released near the fish survey sites. However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable. For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
